\papertitle

### 2012-10-12 manuscript.tex
fixed sigfigs

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling 
wings\footnote{\url{http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{Expand! Accredit it to Stan Baek!} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

@@

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on the H$^2$Bird using 
a particle filter-based motion tracking algorithm. This pose estimate is 
the feedback input to the cooperative visual servoing feedback loop (Sec. \ref{sec:visual_servoing_concept}).

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing_concept}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO ryan
The task we chose to test our cooperative visual servoing system with is a 
simple target seeking one: the H$^2$Bird must fly through a specified obstacle,
in this case, a wooden frame meant to simulate a window. As the H$^2$Bird does
cannot detect the target on its own, it depends on remote guidance from the
base station. Ground truth data was collected via a motion capture system in
the test room. A sketch of the experimental setup is shown below in Fig.~\ref{fig:experiment_cartoon}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal using both analytical and empirical methods. We conducted 
experiments to validate this model.

@@

%----------------------------------------------------------------------------%
\subsection{Ornithopter Attitude Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

@@

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.94782}{1+0.61998s}
\end{equation}
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron

\subsubsection{Reachability Model}
%TODO make these span the page, with identical scales/style

@@

\subsubsection{Experimental Validation}
To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from a window along the
edges of the camera image frame. We began each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 79\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending upon the PID
tuning and the distance from the camera. Tracking noise can also cause passage
negotiation to fail.

>>>>

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling 
wings\footnote{\url{http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{Expand! Accredit it to Stan Baek!} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

@@

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on the H$^2$Bird using 
a particle filter-based motion tracking algorithm. This pose estimate is 
the feedback input to the cooperative visual servoing feedback loop (Sec. \ref{sec:visual_servoing_concept}).

@@

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Model}

%----------------------------------------------------------------------------%
\subsection{Ornithopter Attitude Control}

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}

%----------------------------------------------------------------------------%
\subsection{System Identification}

%............................................................................%
\subsubsection{Ornithoper Attitude Control}

%............................................................................%
\subsubsection{Ground Station Pose Estimation}

%............................................................................%
\subsubsection{Cooperative Visual Servoing}

%----------------------------------------------------------------------------%
\subsection{Model Verification}

The task we chose to test our cooperative visual servoing system with is a 
simple target seeking one: the H$^2$Bird must fly through a specified obstacle,
in this case, a wooden frame meant to simulate a window. As the H$^2$Bird does
cannot detect the target on its own, it depends on remote guidance from the
base station. Ground truth data was collected via a motion capture system in
the test room. A sketch of the experimental setup is shown below in Fig.~\ref{fig:experiment_cartoon}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal using both analytical and empirical methods. We conducted 
experiments to validate this model.

@@

%----------------------------------------------------------------------------%
\subsection{System Identification}

%............................................................................%
\subsubsection{Ornithoper Attitude Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

@@

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.95}{1+0.62s}
\end{equation}
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

@@

%............................................................................%
\subsubsection{Ground Station Pose Estimation}

%............................................................................%
\subsubsection{Cooperative Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron

%TODO make these span the page, with identical scales/style

@@

To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from a window along the
edges of the camera image frame. We began each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 80\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending upon the PID
tuning and the distance from the camera. Tracking noise can also cause passage
negotiation to fail.

%----------------------------------------------------------------------------%
\subsection{Model Verification}
